---
output: github_document
---

# mlr3learners.drat

[`drat`](https://github.com/eddelbuettel/drat) package repository for the [mlr3learners.drat](https://github.com/mlr3learners/mlr3learners.drat) project.  
Install mlr3 learners from this repository using

```{r, eval = FALSE}
install.packages(..., repos = "https://mlr3learners.github.io/mlr3learners.drat")
```

To omit having to pass the `repos` argument every single time, add the following to your `.Rprofile`:

```{r, eval=FALSE}
options(repos = structure(c(getOption("repos"),
  mlr3learners = "https://mlr3learners.github.io/mlr3learners.drat")))
```

This will append this drat repo to your list of available repositories which `install.packages()` will check when trying to install a package.
If you want a c/p command for this: The following will append the line above to your `~/.Rprofile` while keeping your currently set CRAN mirror:

```{r}
cran = getOption('repos')[['CRAN']] 
write(sprintf("options(repos = structure(c(CRAN = '%s',
  mlr3learners = 'https://mlr3learners.github.io/mlr3learners.drat')))",
   cran),
  file = "~/.Rprofile", append = TRUE)
```

**Note: Restart your R session to make use of the new option.**

With this, you are able to install any learner from the [mlr3learners](https://github.com/mlr3learners) organization as simple as 

```{r, eval = FALSE}
install.packages("mlr3learners.kernlab")
```

## Available packages

List of all available learners in this organization

```{r echo=FALSE}
# need to exclude ksvm manually because its still somewhere in the index but not available anymore (renamed to kernlab)
setdiff(as.character(available.packages(repos = "https://mlr3learners.github.io/mlr3learners.drat")[, 1]), c("mlr3learners.ksvm", "mlr3learners.C50"))
```

## How it works

The package sources and binaries of the listed packages are build by the respective learner packages with the following logic:

- During a CI run when the version does not contain a devel indicator (i.e. .9000)
- On the first of each month

Binaries are build for the current R release and the previous release.
Depending on the release date of a new major or minor R version it may take a while until the new binaries are available.
The binaries are (re-)build on the first of each month.

The work behind the scenes is highly simplified by packages [{tic}](https://github.com/ropensci/tic) and [{drat}](https://github.com/eddelbuettel/drat).

### How to add a mlr3learner to {mlr3learners.drat}

1. Check if you belong to the [mlr3learners.drat team](https://github.com/orgs/mlr3learners/teams/mlr3learners-drat) of the mlr3learners organization.
   If not, ask @pat-s to add you - otherwise, you do not have permission to add deploy keys to this repository.

1. Make sure you have a `GITHUB_PAT` set for the GitHub API calls.
  If you do not know what this is, read `?usethis::browse_github_token()`.

1. Make sure your repo already uses GitHub Actions. 
  If not, call `tic::use_ghactions_yml(deploy = TRUE)`.
  
1. Source `init_mlr3learner_drat_deploy()` from [this Gist](https://gist.github.com/pat-s/be7b0ebc6953726d5a51a171742c3e21) and call the function with the name of the repo, e.g. `init_mlr3learner_drat_deploy("mlr3learners.mboost")`.
  This will add a private key as a "secret" to your repo and a public deploy key to [mlr3learners/mlr3learners.drat](https://github.com/mlr3learners/mlr3learners.drat), making it possible to deploy to the latter from your repo.
  
1. Now the macOS and Windows runners will push their binaries to mlr3learners.drat for every no-devel version (i.e. versions without .9000 at the end).
  The Linux runner will push the `.tar.gz` file to install the learner from source.
 
**Note**

It is very important to only init one CI run per release and then switch directly to a dev version.
Otherwise, binaries will be pushed during every CI run, bloating up the repo size of mlr3learners/mlr3learners.drat](https://github.com/mlr3learners/mlr3learners.drat).
   
